### 2020-06-12 README.Rmd
changed readme

The package `covid19census` provides functions to extract COVID-19 cases, deaths, hospitalizations and test of U.S. and Italy at the county and regional level, respectively, and then combine them with other population metrics (age, sex, prevalence of chronic conditions, income indexes, access to health services and many others).

>>>>

The package `covid19census` provides functions to extract COVID-19 cases, deaths, hospitalizations and test of U.S. and Italy at the county and regional level, respectively, and then combines them with other population metrics (age, sex, prevalence of chronic conditions, income indexes, access to health services and many others).

*Note that the package has not been made by, and is not part of the covid19.cesus.gov website.*
